\bf The EPEC Model

### 2021-08-28 Documentation/EPEC_Model.tex
Added Poem terms

+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k\nonumber\\[0.5ex]&\phantom{=====} +\frac{\alpha_{b\,e\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{e}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_e}^{\,2}+W_k^{\,2}}\right)X_k+\frac{\alpha_{b\,i\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_i}^{\,2}+\hat{W}_k^{\,2}}\right)X_k\nonumber\\[0.5ex]
&\phantom{=====}+\frac{\alpha_{c\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}\right)X_k+\frac{\alpha_{p\,k}}{\hat{W}_k^{\,3}}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{W}_k^{\,2}}\right)^2 X_k,\\[0.5ex]

@@

+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k\nonumber\\[0.5ex]&\phantom{=====} +\frac{\alpha_{b\,e\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{e}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_e}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k+\frac{\alpha_{b\,i\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{\rho}_{\theta_i}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k\nonumber\\[0.5ex]
&\phantom{=====}+\frac{\alpha_{c\,k}}{\hat{W}_k}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}\right)Y_k+\frac{\alpha_{p\,k}}{\hat{W}_k^{\,3}}\left(\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_{i}\,k}\,\hat{W}_{n_e\,k}+\hat{W}_k^{\,2}}\right)^2 Y_k,\label{e22}

@@

@@

\hat{\rho}_{\theta\,e} &= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
\hat{\rho}_{\theta\,i} &= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]

@@

\omega_{\mit\Omega}(r)&= \frac{e\,g\,B_0\,s\,q}{m_i}.

@@

mass density profile.

The EPEC resonant plasma response model interpolates smoothly
between the linear regime and the
nonlinear Rutherford regime. The linear regime corresponds to $\hat{W}_k\ll\hat{\delta}_k$, whereas the nonlinear
region corresponds to $\hat{W}_k\gg\hat{\delta}_k$.

@@

\subsection{Natural Frequencies}
According to linear tearing mode theory, in the absence of the RMP, the natural frequency of the tearing mode resonant at the $k$th resonant surface is given by
\begin{equation}\label{elin}
 \varpi_{{\rm linear}\,k} = - n\,(\omega_E+\omega_{\ast\,e})_{r_k}.
\end{equation}
According to nonlinear tearing mode theory, in the absence of the RMP, 
the natural frequency of the tearing mode resonant at the $k$th resonant surface is given by
\begin{equation}\label{e28y}
 \varpi_{{\rm nonlinear}\,k}=  -n\,(\omega_E+\omega_{\ast\,i}+\omega_{{\rm nc}\,i})_{r_k}.
 \end{equation}

Given that our resonant plasma response model interpolates smoothly between the linear regime ($\hat{W}_k\ll \hat{\delta}_k$) and the nonlinear
regime ($\hat{W}_k\gg \hat{\delta}_k$), it makes sense to adopt a model for the natural frequency that does the same. Hence, the EPEC model for the natural frequency is
\begin{equation}\label{ecomp}
\varpi_{k\,0} = \frac{\hat{\delta}_k\,\varpi_{{\rm linear}\,k} +\hat{W}_k\,\varpi_{{\rm nonlinear}\,k}}{\hat{\delta}_k+\hat{W}_k}.
\end{equation}

>>>>

+\hat{\varpi}_k\,Y_k\right)= \sum_{k'=1,K}\hat{E}_{kk'}\,(\cos\xi_{kk'}\,X_{k'}  -\sin\xi_{kk'}\,Y_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\cos\zeta_k\nonumber\\[0.5ex]&\phantom{=====}+\left(f_{b\,k} +f_{c\,k}+f_{p\,k}-f_{s\,k}\right)X_k,\\[0.5ex]

@@

+\sin\xi_{kk'}\,X_{k'}) + \hat{E}_{kk}\,\hat{\chi}_k\,\sin\zeta_k\nonumber\\[0.5ex]&\phantom{=====}+\left(
f_{b\,k} +f_{c\,k}+f_{p\,k}-f_{s\,k}\right)Y_k,\label{e22}

@@

f_{b\,k} &= f_{b\,e\,k}+f_{b\,i\,k},\\[0.5ex]
f_{b\,e\,k} &= \alpha_{b\,e\,k}\left(f_{b\,T_e\,k} + f_{b\,n_e\,k}\right),\\[0.5ex]
f_{b\,i\,k} &= \alpha_{b\,i\,k}\left(f_{b\,T_i\,k} + f_{b\,n_i\,k}\right),\\[0.5ex]
f_{b\,T_e\,k}&=\left(\frac{\eta_e}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_e\,k}^{\,2}+\hat{\rho}_{\theta\,e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,n_e\,k}&=\left(\frac{1}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_i\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{b\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{\rho}_{\theta\,i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{c\,k} &= \alpha_{c\,k}\left(f_{c\,T_e\,k} + f_{c\,n_e\,k} + f_{c\,T_i\,k} + f_{c\,n_i\,k}\right),\\[0.5ex]
f_{c\,T_e\,k}&=\left(\frac{n_e}{n_e+n_i}\,\frac{\eta_e}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{c\,n_e\,k}&=\left(\frac{n_e}{n_e+n_i}\,\frac{1}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{c\,T_i\,k}&=\left(\frac{n_i}{n_e+n_i}\,\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{T_i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{c\,n_i\,k}&=\left(\frac{n_i}{n_e+n_i}\,\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{p\,k} &= \alpha_{p\,k}\left(f_{p\,T_i\,k} + f_{p\,n_i\,k}\right),\\[0.5ex]
f_{p\,T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{(\hat{W}_{T_i\,k}^{\,2}+\hat{W}_k^{\,2})^{\,2}},\\[0.5ex]
f_{p\,n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k}{(\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2})^{\,2}},\\[0.5ex]

@@

\hat{\rho}_{\theta\,e\, k} &= \left(\frac{{\cal I}\,\rho_{\theta\,e}}{2\,r}\right)_{r_k}=\left(\frac{2\,{\cal I}\,v_{T\,e}\,m_e\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]
\hat{\rho}_{\theta\,i\,k} &= \left(\frac{{\cal I}\,\rho_{\theta\,i}}{2\,r}\right)_{r_k}= \left(\frac{2\,{\cal I}\,v_{T\,i}\,m_i\,q\,R_0}{e\,B_0\,g\,r^{\,2}}\right)_{r_k},\\[0.5ex]

@@

\omega_{\mit\Omega}(r)&= \frac{e\,g\,B_0\,s\,q}{m_i},\\[0.5ex]
f_{s\,k} &=\frac{f_{s\,1\,k} \,\hat{W}_{T_e\,k}^{\,2}+ f_{s\,2\,k} \,\hat{W}_k^{\,2}}{\hat{W}_{T_e\,k}^{\,2}+ \hat{W}_k^{\,2}},\\[0.5ex]
f_{s\,1\,k} &= P_{1\,k}\,\frac{W_k}{r_k}\,\ln\left(\frac{r_k}{W_k}\right)+ P_{2\,k}\,\frac{W_k}{r_k},\\[0.5ex]
f_{s\,2\,k} &= P_{3\,k}\,\frac{W_k}{r_k},\\[0.5ex]
P_{1\,k} &= 0.41\,A_k^{\,2},\\[0.5ex]
P_{2\,k} &= 0.41\left(A_k^{\,2}\left[\ln\left(\frac{1}{r_k}\right)+4.85\right] - \frac{{\mit\Sigma}_k'\,A_k}{2} - B_k - 0.44\,A_k\right),\\[0.5ex]
P_{3\,k} &= 0.8\,A_k^{\,2} - 0.27\,B_k-0.09\,A_k,\\[0.5ex]
A_k &= -\left(\frac{r\,q\,\hat{J}_\phi'}{s}\right)_{r_k},\\[0.5ex]
B_k &= -\left(\frac{r^{\,2}\,q\,\hat{J}_\phi''}{s}\right)_{r_k}.

@@

mass density profile. Finally,
\begin{equation}
\hat{J}_\phi(r) = - \frac{\mu_0\,R_0\,R}{B_0}\,\frac{dP}{d{\mit\Psi}_p} - R_0^{\,2}\,B_0\,g\,\frac{dg}{d{\mit\Psi}_p},
\end{equation}
where $P({\mit\Psi}_p)$ is the total plasma pressure,  the previous expression is evaluated on the outboard mid-plane, and
$\hat{J}_\phi'\equiv d\hat{J}_\phi/dr$, $\hat{J}_\phi''\equiv d^{\,2}\hat{J}_\phi/dr^{\,2}$.

The quantity ${\mit\Sigma}_k'$ is
defined as
\begin{equation}
{\mit\Sigma}_k' = \lim_{\delta\rightarrow 0}\left[\left.\frac{r\,\psi'}{\psi}\right|_{r_k-\delta}+ \left.\frac{r\,\psi'}{\psi}\right|_{r_k+\delta}
-2\,A_k\,(1+\ln\delta)\right],
\end{equation}
where $\psi(r)$ is the solution of 
\begin{equation}
\frac{d^{\,2}\psi}{dr^{\,2}}+ \frac{1}{r}\,\frac{d\psi}{dr}-\frac{m^{\,2}}{r^{\,2}}\,\psi - \frac{\hat{J}_\phi'\,\psi}{r\,(1/q-n/m_k)}=0
\end{equation}
that is well=behaved at $r=0$, and satisfies $r\,\psi'/\psi = -m$ at $r=r_{100}$. Here, $\psi'\equiv d\psi/dr$.

Note that the EPEC resonant plasma response model interpolates smoothly
between the linear regime and the
nonlinear Rutherford regime. The linear regime corresponds to $\hat{W}_k\ll\hat{\delta}_k$, whereas the nonlinear
region corresponds to $\hat{W}_k\gg\hat{\delta}_k$.

@@

\subsection{Natural Frequencies}
According to linear tearing mode theory, in the absence of the RMP, the natural frequency of the tearing mode resonant at the $k$th resonant surface is given by
\begin{equation}\label{elin}
 \varpi_{e,k} = - n\,(\omega_E+\omega_{\ast\,e})_{r_k}.
\end{equation}
According to nonlinear tearing mode theory, in the absence of the RMP, 
the natural frequency of the tearing mode resonant at the $k$th resonant surface is given by
\begin{equation}\label{e28y}
 \varpi_{i\,k}=  -n\,(\omega_E+\omega_{\ast\,i}+\omega_{{\rm nc}\,i})_{r_k}.
 \end{equation}
 It is also helpful to define
 \begin{equation}
 \varpi_{E\,k}=  -n\,(\omega_E)_{r_k}.
 \end{equation}

The EPEC model for the natural frequency is
\begin{equation}\label{ecomp}
\varpi_{k\,0} = \varpi_{E\,k} + (\varpi_{e\,k} - \varpi_{E\,k})\,f_{e\,k} + (\varpi_{i\,k} - \varpi_{E\,k})\,f_{i\,k},
\end{equation}
where
\begin{align}
f_{e\,k}&= f_{T_e\,k}+ f_{n_e\,k},\\[0.5ex]
f_{i\,k}&= f_{T_i\,k}+ f_{n_i\,k},\\[0.5ex]
f_{T_e\,k}&=\left(\frac{\eta_e}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_{T_e\,k}^{\,2}}{\hat{W}_{T_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{n_e\,k}&=\left(\frac{1}{1+\eta_e}\right)_{r_k}\,\frac{\hat{W}_{n_e\,k}^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{T_i\,k}&=\left(\frac{\eta_i}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k^{\,2}}{\hat{W}_{T_i\,k}^{\,2}+\hat{W}_k^{\,2}},\\[0.5ex]
f_{n_i\,k}&=\left(\frac{1}{1+\eta_i}\right)_{r_k}\,\frac{\hat{W}_k^{\,2}}{\hat{W}_{n_e\,k}^{\,2}+\hat{W}_k^{\,2}}.
\end{align}
